\documentclass{article}

\usepackage[english]{babel}
\usepackage{eurosym}
\usepackage{iflang}
\usepackage{resume}

\begin{document}

\selectlanguage{english}

\name{\bf EDGAR RIBA}

\begin{llist}
\label{Education}
\sectiontitle{Education}

\employer{UNIVERSITAT AUTONOMA DE BARCELONA} \location{Barcelona, Spain}
\dates{10/2015--now}
Ph.D. in Computer Science\\
Dissertation: \textit{Depth estimation with deep nets and geometric computer vision}.\\
Advisor: Daniel Ponsa.\\
Research Topics: Deep Learning, Local Features, Camera Pose and depth estimation.

\employer{UNIVERSITAT POLITECNICA DE CATALUNYA} \location{Barcelona, Spain}
\dates{07/2012--06/2015}
M.S. in Automatic Control and Robotics.\\
Dissertation: \textit{Implementation of a 3D pose estimation algorithm}.\\
Advisors: Adrian Penate and Francesc Moreno-Noguer.

\employer{UNIVERSITAT POLITECNICA DE CATALUNYA} \location{Barcelona, Spain}
\dates{07/2008--06/2012}
B.S. in Geomatic and Surveying Engineering.


% Research Experience
\label{Work Experience}
\sectiontitle{Work Experience}
\vspace{-0.33cm}

\employer{ARRAIY, Inc.}\location{Barcelona, Spain.}
\dates{11/2017--now}
PhD candidate and Research Engineering Intern
\vspace{-0.33cm}
\begin{itemize}
 \item remotely working on research for depth estimation with deep nets and 3D geometric computer vision for VFX content generation.
\end{itemize}

\employer{OPENCV FOUNDATION}\location{}
\dates{04/2018--now}
Member of the Board of the OpenCV library fundation
\vspace{-0.33cm}
\begin{itemize}
 \item representing the OpenCV library in public events to advertise the Open Computer Vision framework (10M downloads).
 \item mentoring collaboration projects (e.g. during Google Summer of Code).
\end{itemize}

\employer{ARRAIY, Inc.}\location{Palo Alto, CA, USA.}
\dates{05/2017--10/2017}
Research Engineering Intern, Geometry group
\vspace{-0.33cm}
\begin{itemize}
 \item developed and integrated an internal framework for differential 3D geometry using deep nets.
\end{itemize}

\employer{COMPUTER VISION CENTER}\location{Barcelona, Spain}
\dates{10/2015--05/2017}
PhD candidate, MultiSpectral Image Analysis and Understanding group
\vspace{-0.33cm}
\begin{itemize}
 \item worked on deep learning applied to local features.
 \item holder of the trainee research staff grant in the CS department at the Universitat Autonoma de Barcelona.
\end{itemize}

\employer{OPENCV}\location{online}
\dates{05/2016--08/2016}
Intern, Google Summer of Code
\vspace{-0.33cm}
\begin{itemize}
 \item integrated tiny-dnn to OpenCV contrib by adding a wrapper to the caffe converter.
 \item fixed bugs in tiny-dnn and developed several new features such as GPU support via OpenCL and NNPACK optimizations.
\end{itemize}

\employer{OPENCV}\location{online}
\dates{05/2015--08/2015}
Intern, Google Summer of Code
\vspace{-0.33cm}
\begin{itemize}
 \item developed the Structure From Motion module using a customized version of Libmv.
\end{itemize}

\employer{ALDEBARAN ROBOTICS}\location{Paris, France}
\dates{02/2015--06/2015}
Intern Software Engineer, Perception team
\vspace{-0.33cm}
\begin{itemize}
 \item designed and implemented an algorithm for people detection and tracking by sensor fusion using ROS, OpenCV and C++.
\end{itemize}

\employer{OPENCV}\location{online}
\dates{05/2014--08/2014}
Intern, Google Summer of Code
\vspace{-0.33cm}
\begin{itemize}
 \item designed and implemented a real time pose estimation algorithm for textured objects.
 \item implemented the PnP method: \textit{A direct least-squares} (DLS) in the calib3d module.
 \item contributed with a tutorial for the calib3d module.
\end{itemize}

\employer{INSTITUT DE ROBOTICA I INFORMATICA INDUSTRIAL (CSIC-UPC) }\location{Barcelona, Spain}
\dates{05/2014--08/2014}
Research Assistant, Perception and Manipulation group
\vspace{-0.33cm}
\begin{itemize}
 \item worked on my masters thesis in geometric computer vision.
\end{itemize}


% Teaching Experience
\label{Teaching Experience}
\sectiontitle{Teaching Experience}

\employer{UNIVERSITAT POLITECNICA DE CATALUNYA}\location{Barcelona, Spain}
310209, {\em Electromagnetism and Optics}, Fall 2007: Teaching Assistant\\
310209, {\em Electromagnetism and Optics}, Spring 2007: Teaching Assistant

\employer{UNIVERSITAT AUTONOMA DE BARCELONA}\location{Barcelona, Spain}
102708, {\em Software Engineering I}, Spring 2016-2018: Teaching Assistant\\

% Professional Activities
\sectiontitle{Professional Activities}
\vspace{-0.4cm}

Student and Mentor of Google Summer of Code mentor from 2014 to 2018.

Member of the board of the official OpenCV foundation.

Mantainer/developer of the tiny-dnn library involved in the core development and design, bug fixes and code review.

Contributed in many Open Source projects such as OpenCV, tiny-dnn, Pytorch, ROS, Object Recognition Kitchen, OpenDroneMap and OpenSfM.

Participated in robotics competitions and campus such as the HUMABOT Robot Competition 2014 during the \textit{IEEE-RAS International Conference on Humanoid Robots} (Madrid, Spain) and the RoCKIn Camp 2014 organized by  La Sapienza University of Rome (Rome, Italy) within the company PAL Robotics.

Co-founder and member of the \textit{La Konfraria de la Vila del Pingui}. An Open Source community, organizing local events and workshops spreading the free software culture.


% Skills
\label{Skills}
\sectiontitle{Skills}
Competence: Comuter Vision (local features, camera pose estimation), Deep Learning, Robotics, Programming.\\
Programming Languages: C++, Python.\\
Programming Libraries: Pytorch, OpenCV, ROS, tiny-dnn. \\
Extra Interests: Git, Docker, Vim, CMake, OpenCL, Android. \\
Languages: Catalan (native), Spanish (native), English  (professional)


% Software
\sectiontitle{Software}
{\em tiny-dnn}: header only, dependency-free deep learning framework in C++11.


% Papers
%\sectiontitle{Journal Articles}
%\input{publications_journals.tex}

\sectiontitle{Papers in Reviewed Proceedings}
\input{publications_articles.tex}

% Relevant Coursework
\label{Relevant Coursework}
\sectiontitle{Relevant Coursework}
- \textit{Object Detection} (Free online course, Universitat Autonoma de Barcelona. Fall 2015)\\
- \textit{Machine Learning} (Free online course, Stanford. Fall 2014)\\
- \textit{Introduction to Robot Operating System (ROS)} (Universitat Politecnica de Catalunya. Spring 2014)

\label{Reference}
\sectiontitle{References}
\input{references.tex}

\end{llist}

{\em Last update: \today}

\end{document}
